---
title: "Hospitals Inpatient Workload 2019"

author:
  - name: Dr Saiful Safuan Md Sani 
    url: https://saifulsafuan.com
    affiliation: Clinical Research Centre & Department of Medicine Hospital Kuala Lumpur
  - name: Dr Cheah Wee Kooi
    affiliation: Clinical Research Centre & Department of Medicine Hospital Taiping
  - name: Dr Yoon Chee Kin
    affiliation: Clinical Research Centre & Department of Medicine Hospital Pulau Pinang
date: "`2022-01-17`"
output: 
  distill::distill_article:
    self_contained: yes
    toc: yes
    toc_depth: 2
---

```{r setup, include=FALSE}
library(knitr)
library(distill)
library(googlesheets)
library(gsheet)
library(dplyr)
library(ggplot2)
library(plotly)
#library(zoo) # moving averages
#library(RcppRoll) # running total
```
```{r chartstudio, include=FALSE}
#Sys.setenv("plotly_username"="dcicantab5")
#Sys.setenv("plotly_api_key"="zY42xxH3ClQIvgjdFZlH")
```

```{r urlshare, include=FALSE}
#### SHARING GEN MED WORKLOAD ####
#library(googlesheets4)
# read_sheet(urlshare, "data_combo_sharegen") #alternative

urlshare <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=710983312"
  #"https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=710983312"  
hosp2019share <- gsheet2tbl(urlshare, "data_combo_sharegen") 
```
```{r, include=FALSE}
hosp2019share$type <- as.factor(hosp2019share$type)
hosp2019share$type <- relevel(hosp2019share$type, "state")

rownames(hosp2019share) <- hosp2019share$hospital
rownames(hosp2019share)

#col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

hosp2019share$hospital <- factor(hosp2019share$hospital,
                   levels = hosp2019share$hospital)

datashare <- arrange(hosp2019share, type, desc(spec_n_per_1000_adm))
```

```{r url, include=FALSE}
#### ALL IN ####
url <- 'https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit?usp=sharing'  
# kkm data from datuk noel thomas from dr cheah wee kooi; email feb 2021
hosp2019 <- gsheet2tbl(url)
hosp2019$type <- as.factor(hosp2019$type)
hosp2019$type <- relevel(hosp2019$type, "state")

rownames(hosp2019) <- hosp2019$hospital
rownames(hosp2019)

col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

hosp2019$hospital <- factor(hosp2019$hospital,
                   levels = hosp2019$hospital)

data <- arrange(hosp2019, desc(spec_n_per_1000_adm))
```
```{r, message=FALSE, echo=FALSE, warning=FALSE, include=FALSE}
levels(hosp2019$hospital)
```
```{r, message=FALSE, echo=FALSE, warning=FALSE, include=FALSE}
str(hosp2019)
```
# Admissions
```{r, fig.cap="Gen Med admissions.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}
#### Current workload
col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

datashare_adm <- arrange(hosp2019share, admission)
datashare_adm$hospital <- factor(datashare_adm$hospital,
                   levels = datashare_adm$hospital)

p <- plot_ly(datashare_adm, y = ~factor(hospital), x = ~admission, alpha = 0.97, size = 7)
subplot(
  add_bars(p, color = ~factor(type), colors = col3,  showlegend = TRUE) 
) %>% layout(
     title = "Admissions <br><sup></sup>",
     yaxis = list(title = "",
     categoryorder = "array",
     categoryarray = ~datashare_adm$hospital, tickfont = list(size = 10)),
     xaxis = list(title = "Number of admissions")
) %>% layout(legend = list(x = 0.77, y = 0.9)) %>% 
 layout(annotations = 
 list(x = 1, y = 0.51, text = "", 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='right', yanchor='auto', xshift=0, yshift=0,
      font=list(size=12, color="grey"))
 )


#options(browser = 'false')
#api_create(p, filename = "hosp2019_admission")
```

<a href="#top">Return to table of contents</a>

# Number of Specialists
```{r, fig.cap="Number of specialists involved in handling Gen Med admissions only.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}

col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

datashare_spec <- arrange(hosp2019share, spec_sharegen)
datashare_spec$hospital <- factor(datashare_spec$hospital,
                   levels = datashare_spec$hospital)

p <- plot_ly(datashare_spec, y = ~factor(hospital), x = ~spec_sharegen, alpha = 0.97, size = 13)
subplot(
  add_bars(p, color = ~factor(type), colors = col3,  showlegend = TRUE) 
) %>% layout(
     title = "Specialists <br><sup></sup>",
     yaxis = list(title = "",
     categoryorder = "array",
     categoryarray = ~datashare_spec$hospital, tickfont = list(size = 10)),
     xaxis = list(title = "Number of specialists")
) %>% layout(legend = list(x = 0.77, y = 0.9)) %>% 
 layout(annotations = 
 list(x = 1, y = 0.51, text = "", 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='right', yanchor='auto', xshift=0, yshift=0,
      font=list(size=12, color="grey"))
 )


#options(browser = 'false')
#api_create(p, filename = "hosp2019_spec_n")
```
<a href="#top">Return to table of contents</a>

# Standardised Workload
```{r, fig.cap="Standardised Inpatient Workload. Denominator is Gen Med admissions.", out.extra="class=external", message=FALSE, echo=FALSE, warning=FALSE}
states <- datashare %>% filter(type == 'state')
states$hospital <- factor(states$hospital)
#str(states)

p_states <- plot_ly(states, y = ~hospital, x = ~spec_n_per_1000_adm, type = 'bar',  name = 'States', color = ~factor(type), colors = col3)
p_states <- p_states %>% add_trace(states, y = ~hospital, x = ~median, 
                      type = 'scatter', 
                      name = 'Median',
                      mode = "lines", 
                      line = list(color = "crimson", dash = 'dot', width = 7), 
                      opacity = 0.97)
p_states <- p_states %>% layout(xaxis = list(title = 'Number of specialists per 1000 admissions'), yaxis = list(title = '', categoryorder = "total ascending", tickfont = list(size = 8)))

#p_states

major <- datashare %>% filter(type == 'major')
major$hospital <- factor(major$hospital)
#str(major)

p_major <- plot_ly(major, y = ~hospital, x = ~spec_n_per_1000_adm, type = 'bar',  name = 'Major', color = ~factor(type), colors = col3)
p_major <- p_major %>% add_trace(major, y = ~hospital, x = ~median, 
                      type = 'scatter', 
                      name = 'Median',
                      mode = "lines", 
                      line = list(color = "crimson", dash = 'dot', width = 7), 
                      opacity = 0.97)
p_major <- p_major %>% layout(xaxis = list(title = 'Number of specialists per 1000 admissions'), yaxis = list(title = '', categoryorder = "total ascending", tickfont = list(size = 8)))

#p_major

minor <- datashare %>% filter(type == 'minor')
minor$hospital <- factor(minor$hospital)
#str(minor)

p_minor <- plot_ly(minor, y = ~hospital, x = ~spec_n_per_1000_adm, type = 'bar',  name = 'Minor', color = ~factor(type), colors = col3)
p_minor <- p_minor %>% add_trace(minor, y = ~hospital, x = ~median, 
                      type = 'scatter', 
                      name = 'Median',
                      mode = "lines", 
                      line = list(color = "crimson", dash = 'dot', width = 7), 
                      opacity = 0.97)
p_minor <- p_minor %>% layout(xaxis = list(title = 'Number of specialists per 1000 admissions'), yaxis = list(title = '', categoryorder = "total ascending", tickfont = list(size = 8)))

#p_minor
```

```{r, fig.cap="Standardised Inpatient Workload. Denominator is Gen Med admissions.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}
subplot(p_states, p_major, p_minor , nrows = 3, heights = c(0.25, 0.5, 0.25), shareX = TRUE, shareY = TRUE) %>% 
  layout(title = list(text = "Standardised Inpatient Workload by Type of Facility"))

#options(browser = 'false')
#api_create(p, filename = "hosp2019_spec_n_per_1000_adm")
```
<a href="#top">Return to table of contents</a>

<br>

$${Adequacy = {Std\;Workload}_{Current} - \displaystyle \left[{Std\;Workload}_{Median} \left( \displaystyle \frac{Workload}{1000}\right)\right]}$$
<br>  

# Specialist Excesses and Shortages: 
## *Current Sharing General Medicine Workload*
```{r, fig.cap="\\label{fig:myfig4}Specialist Excesses and Shortages. Negative values are shortages, and positive values are excesses. Calculation of the value for each hospital is by deducting the median standardised workload (of the respective type of facility) from a hospital's current standardised workload. The number in shortage/excess is then derived using that hospital's current workload.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}

col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

datashare <- arrange(hosp2019share, spec_adequacy)
datashare$hospital <- factor(datashare$hospital,
                   levels = datashare$hospital)

p <- plot_ly(datashare, y = ~factor(hospital), x = ~spec_adequacy, alpha = 0.97, size = 13)
subplot(
  add_markers(p, color = ~factor(type), colors = col3,  showlegend = TRUE) 
) %>% layout(
     title = "Specialist Excesses and Shortages",
     yaxis = list(title = "",
     categoryorder = "array",
     categoryarray = ~datashare$hospital, tickfont = list(size = 8)),
     xaxis = list(title = "Number of specialists")
) %>% layout(legend = list(x = 0.77, y = 0.8))
```
<a href="#top">Return to table of contents</a>

# Specialist Excesses and Shortages: 
## *All-in*
```{r, fig.cap="Specialist Excesses and Shortages. Negative values are shortages, and positive values are excesses, relative to the median of the corresponding hospital type. Calculation of the value for each hospital is by deducting the median standardised workload (of the respective type of facility) from a hospital's current standardised workload. The number in shortage/excess is then derived for that hospital's current workload. ", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}

col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

data <- arrange(hosp2019, spec_adequacy)
data$hospital <- factor(data$hospital,
                   levels = data$hospital)

p <- plot_ly(data, y = ~factor(hospital), x = ~spec_adequacy, alpha = 0.97, size = 13)
subplot(
  add_markers(p, color = ~factor(type), colors = col3,  showlegend = TRUE) 
) %>% layout(
     title = "Specialist Excesses and Shortages",
     yaxis = list(title = "",
     categoryorder = "array",
     categoryarray = ~data$hospital, tickfont = list(size = 8)),
     xaxis = list(title = "Number of specialists")
) %>% layout(legend = list(x = 0.77, y = 0.8))
```
<a href="#top">Return to table of contents</a>

# General Medicine & Subspecialties
```{r urlgensub, include=FALSE}
urlgensub <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=565087130"
  #"https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=710983312"  
gensub <- gsheet2tbl(urlgensub, "gen_subs") 
```
```{r, include=FALSE}
gensub$type <- as.factor(gensub$type)
gensub$type <- relevel(gensub$type, "state")

rownames(gensub) <- gensub$hospital

#col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

gensub$hospital <- factor(gensub$hospital,
                   levels = gensub$hospital)

datagensub <- arrange(gensub, type, desc(Subs_prop))
```
```{r states_gs, message=FALSE, echo=FALSE, warning=FALSE}
states_gs <- datagensub %>% filter(type == 'state')
states_gs <- arrange(states_gs, type, Subs_prop)
p_states_gs <- plot_ly(states_gs, y = ~hospital, 
                       x = ~Subs_prop*100,
                       type = 'bar',
                       name = "States Subs Prop",
                       color = ~type,
                       colors = col3) %>% 
  add_trace(x = ~GenMed_prop*100,
            name = "States Gen Med Prop",
            opacity = 0.5) %>% 
  layout(yaxis = list(title = "", categoryorder = "array", categoryarray =states_gs$hospital, tickfont = list(size = 8)), 
         barmode = "stack",
         xaxis = list(title = "Proportion", titlefont = list(size=8), tickfont = list(size=8)))

#p_states_gs
```

```{r major_gs, message=FALSE, echo=FALSE, warning=FALSE}
major_gs <- datagensub %>% filter(type == 'major')
major_gs <- arrange(major_gs, type, Subs_prop)
p_major_gs <- plot_ly(major_gs, y = ~hospital, 
                       x = ~Subs_prop*100,
                       type = 'bar',
                       name = "Major Subs Prop",
                       color = ~type,
                       colors = col3) %>% 
  add_trace(x = ~GenMed_prop*100,
            name = "Major Gen Med Prop",
            opacity = 0.5) %>% 
  layout(yaxis = list(title = "", categoryorder = "array", categoryarray =major_gs$hospital, tickfont = list(size = 8)), 
         barmode = "stack",
         xaxis = list(title = "Proportion", titlefont = list(size=8), tickfont = list(size=8)))

#p_major_gs
```

```{r minor_gs, message=FALSE, echo=FALSE, warning=FALSE}
minor_gs <- datagensub %>% filter(type == 'minor')
minor_gs <- arrange(minor_gs, type, Subs_prop)
p_minor_gs <- plot_ly(minor_gs, y = ~hospital, 
                       x = ~Subs_prop*100,
                       type = 'bar',
                       name = "Minor Subs Prop",
                       color = ~type,
                       colors = col3) %>% 
  add_trace(x = ~GenMed_prop*100,
            name = "Minor Gen Med Prop",
            opacity = 0.5) %>% 
  layout(yaxis = list(title = "", categoryorder = "array", categoryarray =minor_gs$hospital, tickfont = list(size = 8)), 
         barmode = "stack",
         xaxis = list(title = "Proportion", titlefont = list(size=8), tickfont = list(size=8)))

#p_minor_gs
```
```{r, fig.cap="General medicine & subspecialties proportions.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}
subplot(p_states_gs, p_major_gs, p_minor_gs , nrows = 3, heights = c(0.25, 0.5, 0.25), shareX = TRUE, shareY = TRUE) %>% 
  layout(title = list(text = "General Medicine & Subspecialties Manpower by Type of Facility"))

#options(browser = 'false')
#api_create(p, filename = "gensub")
```
<a href="#top">Return to table of contents</a>

***

# Case studies
## Case Study 1 - Drilldown QE

```{r}
library(kableExtra)
sometext <- strsplit(paste0(
  "excess of 18 specialists"
), " ")[[1]]
text_formatted <- paste(
  text_spec(sometext, color = "green", bold = TRUE),
  collapse = " ")

# To display the text, type `r text_formatted` outside of the chunk
```

* *Current Sharing workload [Fig 4](#current-sharing-general-medicine-workload):* `r text_formatted`. 
  + Standardised workload based on gen med admissions only, for QE is 3.5 specialists per 1000 admissions (Median for all state hospitals 2.2). 
  
```{r}
library(kableExtra)
sometext <- strsplit(paste0(
  "excess of 17 specialists"
), " ")[[1]]
text_formatted <- paste(
  text_spec(sometext, color = "green", bold = TRUE),
  collapse = " ")

# To display the text, type `r text_formatted` outside of the chunk
```

* *All in workload [Fig 5](#all-in):* `r text_formatted`.
  + Standardised workload based on all in admissions, for QE is 3.9 specialists per 1000 admissions (Median for all state hospitals 2.7).
* Specialty composition: 55% (30) subs, 45% (25) gen med [Fig 6](#general-medicine-subspecialties).
* Workload involvement: 
  + Gen med admissions handled by GenMed (25), Gastroenterology (7), Geriatrics (1), Haematology (4) and Infectious Disease (1), and Rheumatology (2); (total: 40).
  + Dermatology (3), Nephrology (5), Neurology (2), and Respiratory (5) are not involved in gen med workload (total: 15).

```{r csqe, message=FALSE, echo=FALSE, warning=FALSE}

urlcsqe <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=1808792127"

csqe <- gsheet2tbl(urlcsqe, "cs_qe")

library(kableExtra)
csqe %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") %>%
  row_spec(1:4, color = "#150377")
```

<a href="#top">Return to table of contents</a>


## Case Study 2 - Drilldown HUS

```{r}
library(kableExtra)
sometext <- strsplit(paste0(
  "excess of 15 specialists"
), " ")[[1]]
text_formatted <- paste(
  text_spec(sometext, color = "green", bold = TRUE),
  collapse = " ")

# To display the text, type `r text_formatted` outside of the chunk
```

* *Current Sharing workload [Fig 4](#current-sharing-general-medicine-workload):* `r text_formatted`.
  + Standardised workload based on gen med admissions only, for HUS is 3.3 specialists per 1000 admissions (Median for all state hospitals 2.2).   

```{r}
library(kableExtra)
sometext <- strsplit(paste0(
  "excess of 20 specialists"
), " ")[[1]]
text_formatted <- paste(
  text_spec(sometext, color = "green", bold = TRUE),
  collapse = " ")

# To display the text, type `r text_formatted` outside of the chunk
```

* *All in workload [Fig 5](#all-in):* `r text_formatted`.
  + Standardised workload based on all in admissions, for HUS is 4.1 specialists per 1000 admissions (Median for all state hospitals 2.7).
* Specialty composition: 68% (39) subs, 32% (18) gen med [Fig 6](#general-medicine-subspecialties).
* Workload involvement: 
  + Gen med admissions handled by GenMed (18), Endocrinology (3) Gastroenterology (1), Geriatrics (2), Haematology (3) and Infectious Disease (3), Rheumatology (6), Nephrology (6), Neurology (4), Palliative (1) and Respiratory (5); (total: 52).
  + Dermatology (5) is not involved in gen med workload (total: 5).

```{r cshus, message=FALSE, echo=FALSE, warning=FALSE}

urlcshus <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=1454553381"

cshus <- gsheet2tbl(urlcshus, "cs_hus")

library(kableExtra)
cshus %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") %>%
  row_spec(1, color = "#150377")
```

<a href="#top">Return to table of contents</a>

## Case Study 3 - Drilldown HKL

```{r}
library(kableExtra)
sometext <- strsplit(paste0(
  "shortage of 7 specialists"
), " ")[[1]]
text_formatted <- paste(
  text_spec(sometext, color = "red", bold = TRUE),
  collapse = " ")

# To display the text, type `r text_formatted` outside of the chunk
```

* *Current Sharing workload [Fig 4](#current-sharing-general-medicine-workload):* `r text_formatted`. 
  + Standardised workload based on gen med admissions only, for HKL is 2.1 specialists per 1000 admissions (Median for all state hospitals 2.2).

```{r}
library(kableExtra)
sometext <- strsplit(paste0(
  "excess of 14 specialists"
), " ")[[1]]
text_formatted <- paste(
  text_spec(sometext, color = "green", bold = TRUE),
  collapse = " ")

# To display the text, type `r text_formatted` outside of the chunk
```

* *All in workload [Fig 5](#all-in):* `r text_formatted`.
  + Standardised workload based on all in admissions, for HKL is 3 specialists per 1000 admissions (Median for all state hospitals 2.7). 
* Specialty composition: 79% (96) subs, 21% (27) gen med [Fig 6](#general-medicine-subspecialties).
* Workload involvement: 
  + Gen med admissions handled by GenMed (16), AAIM (11), Endocrinology (11), Gastroenterology (11), Geriatrics (17), Haematology (2) and Infectious Disease (3), Palliative (3) and Rheumatology (2); (total: 76).
  + Dermatology (19), Nephrology (18), and Neurology (10) are not involved in gen med workload (total: 47).

```{r cshkl, message=FALSE, echo=FALSE, warning=FALSE}

urlcshkl <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=898591304"

cshkl <- gsheet2tbl(urlcshkl, "cs_hkl")

library(kableExtra)
cshkl %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") %>%
  row_spec(1:3, color = "#150377")
```
<a href="#top">Return to table of contents</a>

## Case Study 4 - Drilldown Serdang


```{r}
library(kableExtra)
sometext <- strsplit(paste0(
  "excess of 5 specialists"
), " ")[[1]]
text_formatted <- paste(
  text_spec(sometext, color = "green", bold = TRUE),
  collapse = " ")

# To display the text, type `r text_formatted` outside of the chunk
```

* *Current Sharing workload [Fig 4](#current-sharing-general-medicine-workload):* `r text_formatted`.
  + Standardised workload based on gen med admissions only, for Serdang is 2 specialists per 1000 admissions (Median for all major hospitals 1.41).  

```{r}
library(kableExtra)
sometext <- strsplit(paste0(
  "excess of 24 specialists"
), " ")[[1]]
text_formatted <- paste(
  text_spec(sometext, color = "green", bold = TRUE),
  collapse = " ")

# To display the text, type `r text_formatted` outside of the chunk
```

* *All in workload [Fig 5](#all-in):* `r text_formatted`.
  + Standardised workload based on all in admissions, for Serdang is 2.7 specialists per 1000 admissions (Median for all major hospitals 1.55).
* Specialty composition: 82% (45) subs, 18% (10) gen med [Fig 6](#general-medicine-subspecialties).
* Workload involvement:  
  + Gen med admissions handled by GenMed (10), Endocrinology (2), Gastroenterology (5), and Infectious Disease (1); (total: 18).
  + Cardiology (14), Dermatology (4), Nephrology (10), Respiratory (8) & Rheumatology (1) are not involved in gen med workload (total: 37).
  + *?Inpatient workload for Dermatology, Respiratory & Rheumatology within gen med admissions.*
  
```{r csserdang, message=FALSE, echo=FALSE, warning=FALSE}

urlcsserdang <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=57638925"

csserdang <- gsheet2tbl(urlcsserdang, "cs_serdang")

library(kableExtra)
csserdang %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") %>%
  row_spec(1:2, color = "rgba(250,128,114,1)")
```
<a href="#top">Return to table of contents</a>

## Case Study 5 - Drilldown Melaka

```{r}
library(kableExtra)
sometext <- strsplit(paste0(
  "shortage of 17 specialists"
), " ")[[1]]
text_formatted <- paste(
  text_spec(sometext, color = "red", bold = TRUE),
  collapse = " ")

# To display the text, type `r text_formatted` outside of the chunk
```

* *Current Sharing workload [Fig 4](#current-sharing-general-medicine-workload):* `r text_formatted`.
  + Standardised workload based on gen med admissions only, for Melaka is 1.4 specialists per 1000 admissions (Median for all state hospitals 2.2).   

```{r}
library(kableExtra)
sometext <- strsplit(paste0(
  "shortage of 21 specialists"
), " ")[[1]]
text_formatted <- paste(
  text_spec(sometext, color = "red", bold = TRUE),
  collapse = " ")

# To display the text, type `r text_formatted` outside of the chunk
```

* *All in workload [Fig 5](#all-in):* `r text_formatted`.
  + Standardised workload based on all in admissions, for Melaka is 1.7 specialists per 1000 admissions (Median for all state hospitals 2.7).
* 49% (17) subs, 51% (18) gen med.
* Specialty composition: see [Fig 6](#general-medicine-subspecialties). 
* Workload involvement: Dermatology is the only sub not involved in gen med workload (2).

```{r csmelaka, message=FALSE, echo=FALSE, warning=FALSE}

urlcsmelaka <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=1173288709"

csmelaka <- gsheet2tbl(urlcsmelaka, "cs_melaka")

library(kableExtra)
csmelaka %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") %>%
  row_spec(5, color = "#150377")
```
<a href="#top">Return to table of contents</a>



