---
title: "Hospitals Inpatient Workload 2019"
author:
  - name: Dr Saiful Safuan Md Sani 
    url: https://saifulsafuan.com
    affiliation: Clinical Research Centre & Department of Medicine Hospital Kuala Lumpur
  - name: Dr Cheah Wee Kooi
    affiliation: Clinical Research Centre & Department of Medicine Hospital Taiping
  - name: Dr Yoon Chee Kin
    affiliation: Clinical Research Centre & Department of Medicine Hospital Pulau Pinang
date: "`2022-05-28`"
output:
  distill::distill_article:
    self_contained: yes
    toc: yes
    toc_float: yes
  pdf_document: 
    toc: true
always_allow_html: yes
---


```{r setup, include=FALSE}
# first pub 17 Jan 2022
library(knitr)
library(distill)
library(googlesheets)
library(gsheet)
library(dplyr)
library(ggplot2)
library(plotly)
library(DT)
library(kableExtra)
#library(zoo) # moving averages
#library(RcppRoll) # running total

#  distill::distill_article:
#    self_contained: yes
#    toc: yes
#    toc_depth: 2
#    _includes: analytics.html

```
```{r chartstudio, include=FALSE}
#Sys.setenv("plotly_username"="dcicantab5")
#Sys.setenv("plotly_api_key"="zY42xxH3ClQIvgjdFZlH")
```

```{r urlshare, include=FALSE}
#### SHARING GEN MED WORKLOAD 7 March 2022####
#library(googlesheets4)
# read_sheet(urlshare, "data_combo_sharegen") #alternative

#urlshare <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=710983312"
  #"https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=710983312"  

urlshare <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=1996562624" ### 7 March 2022
hosp2019share <- gsheet2tbl(urlshare, "data_combo_sharegen_7mac2022") 

hosp2019share$type <- as.factor(hosp2019share$type)
hosp2019share$type <- relevel(hosp2019share$type, "state")

rownames(hosp2019share) <- hosp2019share$hospital
rownames(hosp2019share)

#col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

hosp2019share$hospital <- factor(hosp2019share$hospital,
                   levels = hosp2019share$hospital)

datashare <- arrange(hosp2019share, type, desc(spec_n_per_1000_adm))
```
```{r, include=FALSE}
### 26 May 2022
urlshare26may2022 <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=49215200"  ### 26 May 2022
hosp2019share26may2022 <- gsheet2tbl(urlshare26may2022, "data_combo_sharegen_26may2022") 
hosp2019share26may2022$type <- as.factor(hosp2019share26may2022$type)
hosp2019share26may2022$type <- relevel(hosp2019share26may2022$type, "state")

rownames(hosp2019share26may2022) <- hosp2019share26may2022$hospital
rownames(hosp2019share26may2022)

#col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

hosp2019share26may2022$hospital <- factor(hosp2019share26may2022$hospital,
                   levels = hosp2019share26may2022$hospital)

datashare26may2022 <- arrange(hosp2019share26may2022, type, desc(spec_n_per_1000_adm))
```
```{r url 7 March 2022, include=FALSE}
#### ALL IN 7 March 2022####
# url <- 'https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit?usp=sharing'  
url <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=1568757140"  ### 7 March 2022
# kkm data from datuk noel thomas from dr cheah wee kooi; email feb 2021
hosp2019 <- gsheet2tbl(url, "data_combo_totman_7mac2022")
hosp2019$type <- as.factor(hosp2019$type)
hosp2019$type <- relevel(hosp2019$type, "state")

rownames(hosp2019) <- hosp2019$hospital
rownames(hosp2019)

col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

hosp2019$hospital <- factor(hosp2019$hospital,
                   levels = hosp2019$hospital)

data <- arrange(hosp2019, desc(spec_n_per_1000_adm))
```
```{r, message=FALSE, echo=FALSE, warning=FALSE, include=FALSE}
levels(hosp2019$hospital)
```
```{r, message=FALSE, echo=FALSE, warning=FALSE, include=FALSE}
str(hosp2019)
```
```{r url 26 May 2022, include=FALSE}
#### ALL IN 26 May 2022####
# url <- 'https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit?usp=sharing'  
url <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=1228314601"  ### 26 May 2022
# kkm data from datuk noel thomas from dr cheah wee kooi; email feb 2021
hosp201926may2022 <- gsheet2tbl(url, "data_combo_totman_26may2022")
hosp201926may2022$type <- as.factor(hosp201926may2022$type)
hosp201926may2022$type <- relevel(hosp201926may2022$type, "state")

rownames(hosp201926may2022) <- hosp201926may2022$hospital
rownames(hosp201926may2022)

col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

hosp201926may2022$hospital <- factor(hosp201926may2022$hospital,
                   levels = hosp201926may2022$hospital)

data26may2022 <- arrange(hosp201926may2022, desc(spec_n_per_1000_adm))
```

# Shared Admissions Workload
```{r, fig.cap="Gen Med admissions.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}
#### Current workload
col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

datashare_adm <- arrange(hosp2019share, admission)
datashare_adm$hospital <- factor(datashare_adm$hospital,
                   levels = datashare_adm$hospital)

p <- plot_ly(datashare_adm, y = ~factor(hospital), x = ~admission, alpha = 0.97, size = 7)
subplot(
  add_bars(p, color = ~factor(type), colors = col3,  showlegend = TRUE) 
) %>% layout(
     title = "Shared Admissions Workload<br><sup></sup>",
     yaxis = list(title = "",
     categoryorder = "array",
     categoryarray = ~datashare_adm$hospital, tickfont = list(size = 10)),
     xaxis = list(title = "Number of admissions")
) %>% layout(legend = list(x = 0.77, y = 0.9)) %>% 
 layout(annotations = 
 list(x = 1, y = 0.51, text = "", 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='right', yanchor='auto', xshift=0, yshift=0,
      font=list(size=12, color="grey"))
 )


#options(browser = 'false')
#api_create(p, filename = "hosp2019_admission")
```

<a href="#top">Return to table of contents</a>

\pagebreak

# Number of Specialists Sharing Admissions Workload 7 March 2022
```{r, fig.cap="Number of specialists sharing admissions workload 7 March 2022.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}

col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

datashare_spec <- arrange(hosp2019share, spec_sharegen)
datashare_spec$hospital <- factor(datashare_spec$hospital,
                   levels = datashare_spec$hospital)

p <- plot_ly(datashare_spec, y = ~factor(hospital), x = ~spec_sharegen, alpha = 0.97, size = 13)
subplot(
  add_bars(p, color = ~factor(type), colors = col3,  showlegend = TRUE) 
) %>% layout(
     title = "Specialists Sharing Admissions Workload 7 March 2022<br><sup></sup>",
     yaxis = list(title = "",
     categoryorder = "array",
     categoryarray = ~datashare_spec$hospital, tickfont = list(size = 10)),
     xaxis = list(title = "Number of specialists")
) %>% layout(legend = list(x = 0.77, y = 0.9)) %>% 
 layout(annotations = 
 list(x = 1, y = 0.51, text = "", 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='right', yanchor='auto', xshift=0, yshift=0,
      font=list(size=12, color="grey"))
 )


#options(browser = 'false')
#api_create(p, filename = "hosp2019_spec_n")
```
<a href="#top">Return to table of contents</a>

\pagebreak

# Number of Specialists Sharing Admissions Workload 26 May 2022
```{r, fig.cap="Number of specialists sharing admissions workload 26 May 2022.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}

col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

datashare_spec26may2022 <- arrange(hosp2019share26may2022, spec_n)
datashare_spec26may2022$hospital <- factor(datashare_spec26may2022$hospital,
                   levels = datashare_spec26may2022$hospital)

p <- plot_ly(datashare_spec26may2022, y = ~factor(hospital), x = ~spec_n, alpha = 0.97, size = 13)
subplot(
  add_bars(p, color = ~factor(type), colors = col3,  showlegend = TRUE) 
) %>% layout(
     title = "Specialists Sharing Admissions Workload 26 May 2022<br><sup></sup>",
     yaxis = list(title = "",
     categoryorder = "array",
     categoryarray = ~datashare_spec26may2022$hospital, tickfont = list(size = 10)),
     xaxis = list(title = "Number of specialists")
) %>% layout(legend = list(x = 0.77, y = 0.9)) %>% 
 layout(annotations = 
 list(x = 1, y = 0.51, text = "", 
      showarrow = F, xref='paper', yref='paper', 
      xanchor='right', yanchor='auto', xshift=0, yshift=0,
      font=list(size=12, color="grey"))
 )


#options(browser = 'false')
#api_create(p, filename = "hosp2019_spec_n")
```
<a href="#top">Return to table of contents</a>

\pagebreak

# Standardised Shared Admissions Workload by Type of Facility 7 March 2022
```{r, fig.cap="Standardised Inpatient Workload. Denominator is Gen Med admissions.", out.extra="class=external", message=FALSE, echo=FALSE, warning=FALSE}
states <- datashare %>% filter(type == 'state')
states$hospital <- factor(states$hospital)
#str(states)

p_states <- plot_ly(states, y = ~hospital, x = ~spec_n_per_1000_adm, type = 'bar',  name = 'States', color = ~factor(type), colors = col3)
p_states <- p_states %>% add_trace(states, y = ~hospital, x = ~median, 
                      type = 'scatter', 
                      name = 'Median',
                      mode = "lines", 
                      line = list(color = "crimson", dash = 'dot', width = 7), 
                      opacity = 0.97)
p_states <- p_states %>% layout(xaxis = list(title = 'Number of specialists per 1000 admissions'), yaxis = list(title = '', categoryorder = "total ascending", tickfont = list(size = 8)))

#p_states

major <- datashare %>% filter(type == 'major')
major$hospital <- factor(major$hospital)
#str(major)

p_major <- plot_ly(major, y = ~hospital, x = ~spec_n_per_1000_adm, type = 'bar',  name = 'Major', color = ~factor(type), colors = col3)
p_major <- p_major %>% add_trace(major, y = ~hospital, x = ~median, 
                      type = 'scatter', 
                      name = 'Median',
                      mode = "lines", 
                      line = list(color = "crimson", dash = 'dot', width = 7), 
                      opacity = 0.97)
p_major <- p_major %>% layout(xaxis = list(title = 'Number of specialists per 1000 admissions'), yaxis = list(title = '', categoryorder = "total ascending", tickfont = list(size = 8)))

#p_major

minor <- datashare %>% filter(type == 'minor')
minor$hospital <- factor(minor$hospital)
#str(minor)

p_minor <- plot_ly(minor, y = ~hospital, x = ~spec_n_per_1000_adm, type = 'bar',  name = 'Minor', color = ~factor(type), colors = col3)
p_minor <- p_minor %>% add_trace(minor, y = ~hospital, x = ~median, 
                      type = 'scatter', 
                      name = 'Median',
                      mode = "lines", 
                      line = list(color = "crimson", dash = 'dot', width = 7), 
                      opacity = 0.97)
p_minor <- p_minor %>% layout(xaxis = list(title = 'Number of specialists per 1000 admissions'), yaxis = list(title = '', categoryorder = "total ascending", tickfont = list(size = 8)))

#p_minor
```

```{r, fig.cap="Standardised Shared Admissions Workload 7 March 2022.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}
subplot(p_states, p_major, p_minor , nrows = 3, heights = c(0.25, 0.5, 0.25), shareX = TRUE, shareY = TRUE) %>% 
  layout(title = list(text = "Standardised Shared Admissions Workload by Type of Facility 7 March 2022"))

#options(browser = 'false')
#api_create(p, filename = "hosp2019_spec_n_per_1000_adm")
```
<a href="#top">Return to table of contents</a>

\pagebreak

# Standardised Shared Admissions Workload by Type of Facility 26 May 2022
```{r, fig.cap="Standardised Inpatient Workload. Denominator is Gen Med admissions.", out.extra="class=external", message=FALSE, echo=FALSE, warning=FALSE}
states <- datashare26may2022 %>% filter(type == 'state')
states$hospital <- factor(states$hospital)
#str(states)

p_states <- plot_ly(states, y = ~hospital, x = ~spec_n_per_1000_adm, type = 'bar',  name = 'States', color = ~factor(type), colors = col3)
p_states <- p_states %>% add_trace(states, y = ~hospital, x = ~median, 
                      type = 'scatter', 
                      name = 'Median',
                      mode = "lines", 
                      line = list(color = "crimson", dash = 'dot', width = 7), 
                      opacity = 0.97)
p_states <- p_states %>% layout(xaxis = list(title = 'Number of specialists per 1000 admissions'), yaxis = list(title = '', categoryorder = "total ascending", tickfont = list(size = 8)))

#p_states

major <- datashare26may2022 %>% filter(type == 'major')
major$hospital <- factor(major$hospital)
#str(major)

p_major <- plot_ly(major, y = ~hospital, x = ~spec_n_per_1000_adm, type = 'bar',  name = 'Major', color = ~factor(type), colors = col3)
p_major <- p_major %>% add_trace(major, y = ~hospital, x = ~median, 
                      type = 'scatter', 
                      name = 'Median',
                      mode = "lines", 
                      line = list(color = "crimson", dash = 'dot', width = 7), 
                      opacity = 0.97)
p_major <- p_major %>% layout(xaxis = list(title = 'Number of specialists per 1000 admissions'), yaxis = list(title = '', categoryorder = "total ascending", tickfont = list(size = 8)))

#p_major

minor <- datashare26may2022 %>% filter(type == 'minor')
minor$hospital <- factor(minor$hospital)
#str(minor)

p_minor <- plot_ly(minor, y = ~hospital, x = ~spec_n_per_1000_adm, type = 'bar',  name = 'Minor', color = ~factor(type), colors = col3)
p_minor <- p_minor %>% add_trace(minor, y = ~hospital, x = ~median, 
                      type = 'scatter', 
                      name = 'Median',
                      mode = "lines", 
                      line = list(color = "crimson", dash = 'dot', width = 7), 
                      opacity = 0.97)
p_minor <- p_minor %>% layout(xaxis = list(title = 'Number of specialists per 1000 admissions'), yaxis = list(title = '', categoryorder = "total ascending", tickfont = list(size = 8)))

#p_minor
```

```{r, fig.cap="Standardised Shared Admissions Workload 26 May 2022.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}
subplot(p_states, p_major, p_minor , nrows = 3, heights = c(0.25, 0.5, 0.25), shareX = TRUE, shareY = TRUE) %>% 
  layout(title = list(text = "Standardised Shared Admissions Workload by Type of Facility 26 May 2022"))

#options(browser = 'false')
#api_create(p, filename = "hosp2019_spec_n_per_1000_adm")
```

# Specialist Excesses and Shortages: 

<br> **Explainer:**
<br>
<br> Based on formula for standardised workload (Std Workload),
<br> 

\begin{equation}
{Std\;Workload = {Number\;of\; specialists} \div \left( \displaystyle \frac{Admissions}{1000}\right) }
(\#eq:StdW)
\end{equation} 

<br> 
<br> *e.g. for a hypothetical State Hospital Ledang which has 60 specialists handling General Medicine workload, with a 30,000 admissions,*
<br> 
$${{Std\;Workload}_{Current} = {60} \div \left( \displaystyle \frac{30000}{1000}\right) = 2.0\;spec\;per\;1000\;admissions}$$
<br> 
<br> *if say for example, the median of standardised workload for all state hospitals is 1.0 spec per 1000 admissions, then rearranging \@ref(eq:StdW),*
<br>

\begin{equation}
{{Number\;of\; specialists}_{Median} = {Std\;Workload}_{Median} \times  \left( \displaystyle \frac{Admissions}{1000}\right) }
(\#eq:StdWn)
\end{equation} 

<br> 
\begin{equation}
{{Number\;of\; specialists}_{Median} = 1.0 \times  \left( \displaystyle \frac{30000}{1000}\right) = 30\;specialists }
\end{equation} 
<br> 

<br> *hence,*

\begin{equation}
{Adequacy = {Number\;of\;specialists}_{Current} - {Number\;of\;specialists}_{Median}}
(\#eq:Adeq)
\end{equation} 

<br> 
$${Adequacy = {60} - {30} = Excess\;30\;specialists}$$
<br>

\pagebreak

## *Shared Admissions Workload 7 March 2022*
```{r, fig.cap="\\label{fig:myfig4}Specialist Excesses and Shortages. Negative values are shortages, and positive values are excesses. Calculation of the value for each hospital is by deducting the median standardised workload (of the respective type of facility) from a hospital's current standardised workload. The number in shortage/excess is then derived using that hospital's current workload.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}

col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

datashare <- arrange(hosp2019share, spec_adequacy7mac2022)
datashare$hospital <- factor(datashare$hospital,
                   levels = datashare$hospital)

p <- plot_ly(datashare, y = ~factor(hospital), x = ~spec_adequacy7mac2022, alpha = 0.97, size = 13)
subplot(
  add_markers(p, color = ~factor(type), colors = col3,  showlegend = TRUE) 
) %>% layout(
     title = "Specialist Excesses and Shortages 7 March 2022",
     yaxis = list(title = "",
     categoryorder = "array",
     categoryarray = ~datashare$hospital, tickfont = list(size = 8)),
     xaxis = list(title = "Number of specialists")
) %>% layout(legend = list(x = 0.77, y = 0.8))
```
<a href="#top">Return to table of contents</a>

\pagebreak

## *Shared Admissions Workload 26 May 2022*
```{r, fig.cap="\\label{fig:myfig4}Specialist Excesses and Shortages. Negative values are shortages, and positive values are excesses. Calculation of the value for each hospital is by deducting the median standardised workload (of the respective type of facility) from a hospital's current standardised workload. The number in shortage/excess is then derived using that hospital's current workload.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}

col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")
col4 <- c(`state` = "red", `major` = "green", `minor` = "yellow")
datashare26may2022 <- arrange(hosp2019share26may2022, spec_adequacy26may2022)
datashare26may2022$hospital <- factor(datashare26may2022$hospital,
                   levels = datashare26may2022$hospital)

p <- plot_ly(datashare26may2022, y = ~factor(hospital), x = ~spec_adequacy26may2022)
subplot(
  add_markers(p, color = ~factor(type), colors = col3,  showlegend = TRUE, alpha = 0.97, size = 13) 
) %>% layout(
     title = "Specialist Excesses and Shortages 26 May 2022",
     yaxis = list(title = "",
     categoryorder = "array",
     categoryarray = ~datashare26may2022$hospital, tickfont = list(size = 8)),
     xaxis = list(title = "Number of specialists")
) %>% layout(legend = list(x = 0.77, y = 0.8))

```
<a href="#top">Return to table of contents</a>

\pagebreak

## *All-in 7 March 2022*
```{r, fig.cap="Specialist Excesses and Shortages 7 March 2022. Negative values are shortages, and positive values are excesses, relative to the median of the corresponding hospital type. Calculation of the value for each hospital is by deducting the median standardised workload (of the respective type of facility) from a hospital's current standardised workload. The number in shortage/excess is then derived for that hospital's current workload. ", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}

col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

data <- arrange(hosp2019, spec_adequacy7mac2022)
data$hospital <- factor(data$hospital,
                   levels = data$hospital)

p <- plot_ly(data, y = ~factor(hospital), x = ~spec_adequacy7mac2022, alpha = 0.97, size = 13)
subplot(
  add_markers(p, color = ~factor(type), colors = col3,  showlegend = TRUE) 
) %>% layout(
     title = "Specialist Excesses and Shortages 7 March 2022",
     yaxis = list(title = "",
     categoryorder = "array",
     categoryarray = ~data$hospital, tickfont = list(size = 8)),
     xaxis = list(title = "Number of specialists")
) %>% layout(legend = list(x = 0.77, y = 0.8))
```
<a href="#top">Return to table of contents</a>

\pagebreak

## *All-in 26 May 2022*
```{r, fig.cap="Specialist Excesses and Shortages 26 May 2022. Negative values are shortages, and positive values are excesses, relative to the median of the corresponding hospital type. Calculation of the value for each hospital is by deducting the median standardised workload (of the respective type of facility) from a hospital's current standardised workload. The number in shortage/excess is then derived for that hospital's current workload. ", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}

col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

data26may2022 <- arrange(hosp201926may2022, spec_adequacy26may2022)
data26may2022$hospital <- factor(data26may2022$hospital,
                   levels = data26may2022$hospital)

p <- plot_ly(data26may2022, y = ~factor(hospital), x = ~spec_adequacy26may2022, alpha = 0.97, size = 13)
subplot(
  add_markers(p, color = ~factor(type), colors = col3,  showlegend = TRUE) 
) %>% layout(
     title = "Specialist Excesses and Shortages 26 May 2022",
     yaxis = list(title = "",
     categoryorder = "array",
     categoryarray = ~data26may2022$hospital, tickfont = list(size = 8)),
     xaxis = list(title = "Number of specialists")
) %>% layout(legend = list(x = 0.77, y = 0.8))
```
<a href="#top">Return to table of contents</a>