---
title: "R Notebook"
output: html_notebook
---

# General Medicine & Subspecialties
```{r urlgensub, include=FALSE}
urlgensub <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=565087130"
  #"https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=710983312"  
gensub <- gsheet2tbl(urlgensub, "gen_subs") 
```
```{r, include=FALSE}
gensub$type <- as.factor(gensub$type)
gensub$type <- relevel(gensub$type, "state")

rownames(gensub) <- gensub$hospital

#col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

gensub$hospital <- factor(gensub$hospital,
                   levels = gensub$hospital)

datagensub <- arrange(gensub, type, desc(Subs_prop))
```
```{r states_gs, message=FALSE, echo=FALSE, warning=FALSE}
states_gs <- datagensub %>% filter(type == 'state')
states_gs <- arrange(states_gs, type, Subs_prop)
p_states_gs <- plot_ly(states_gs, y = ~hospital, 
                       x = ~Subs_prop*100,
                       type = 'bar',
                       name = "States Subs Prop",
                       color = ~type,
                       colors = col3) %>% 
  add_trace(x = ~GenMed_prop*100,
            name = "States Gen Med Prop",
            opacity = 0.5) %>% 
  layout(yaxis = list(title = "", categoryorder = "array", categoryarray =states_gs$hospital, tickfont = list(size = 8)), 
         barmode = "stack",
         xaxis = list(title = "Proportion", titlefont = list(size=8), tickfont = list(size=8)))

#p_states_gs
```

```{r major_gs, message=FALSE, echo=FALSE, warning=FALSE}
major_gs <- datagensub %>% filter(type == 'major')
major_gs <- arrange(major_gs, type, Subs_prop)
p_major_gs <- plot_ly(major_gs, y = ~hospital, 
                       x = ~Subs_prop*100,
                       type = 'bar',
                       name = "Major Subs Prop",
                       color = ~type,
                       colors = col3) %>% 
  add_trace(x = ~GenMed_prop*100,
            name = "Major Gen Med Prop",
            opacity = 0.5) %>% 
  layout(yaxis = list(title = "", categoryorder = "array", categoryarray =major_gs$hospital, tickfont = list(size = 8)), 
         barmode = "stack",
         xaxis = list(title = "Proportion", titlefont = list(size=8), tickfont = list(size=8)))

#p_major_gs
```

```{r minor_gs, message=FALSE, echo=FALSE, warning=FALSE}
minor_gs <- datagensub %>% filter(type == 'minor')
minor_gs <- arrange(minor_gs, type, Subs_prop)
p_minor_gs <- plot_ly(minor_gs, y = ~hospital, 
                       x = ~Subs_prop*100,
                       type = 'bar',
                       name = "Minor Subs Prop",
                       color = ~type,
                       colors = col3) %>% 
  add_trace(x = ~GenMed_prop*100,
            name = "Minor Gen Med Prop",
            opacity = 0.5) %>% 
  layout(yaxis = list(title = "", categoryorder = "array", categoryarray =minor_gs$hospital, tickfont = list(size = 8)), 
         barmode = "stack",
         xaxis = list(title = "Proportion", titlefont = list(size=8), tickfont = list(size=8)))

#p_minor_gs
```
```{r, fig.cap="General medicine & subspecialties proportions.", out.extra="class=external",  fig.width=8, fig.height=8, message=FALSE, echo=FALSE, warning=FALSE}
subplot(p_states_gs, p_major_gs, p_minor_gs , nrows = 3, heights = c(0.25, 0.5, 0.25), shareX = TRUE, shareY = TRUE) %>% 
  layout(title = list(text = "General Medicine & Subspecialties Manpower by Type of Facility"))

#options(browser = 'false')
#api_create(p, filename = "gensub")
```
<a href="#top">Return to table of contents</a>

***

# Case studies
## Case Study 1 - Drilldown QE  


***Subs_prop:*** *proportion of subs*
<br> ***GenMed_prop:*** *proportion of gen med*
<br> ***Total:*** *total number of specialists*
<br> ***Median_current:*** *median standardised workload based on current gen med work sharing*
<br> ***ES_current:*** *excess/shortage of specialists based on current gen med work sharing*
<br> ***Median_all:*** *median standardised workload based on all subs contributing to gen med work*
<br> ***ES_all:*** *excess/shortage of specialists based on all subs contributing to gen med work*

```{r}
url_cases <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=1867701472"

cases <- gsheet2tbl(url_cases, "casestudy")  

cases$type <- as.factor(cases$type)
cases$type <- relevel(cases$type, "state")

rownames(cases) <- cases$hospital

cases$hospital <- factor(cases$hospital,
                   levels = cases$hospital)

cases %>%
  filter(hospital=="QUEEN ELIZABETH") %>%
  kbl("html", align = "c", escape = F) %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 10, position = "center") %>%
  kable_paper(full_width = F) %>%
  column_spec(7, color = "white", bold = T,
              background = ifelse(cases$ES_current < 0, "red", "green"),
              popover = paste("am:", cases$Total)) %>%
  column_spec(9, color = "white", bold = T,
              background = ifelse(cases$ES_all < 0, "red", "green"),
              popover = paste("am:", cases$Total))
```

```{r csqe, message=FALSE, echo=FALSE, warning=FALSE}

urlcsqe <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=1808792127"

csqe <- gsheet2tbl(urlcsqe, "cs_qe")


csqe %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") %>%
  row_spec(1, color = "#150377") 
```
*QE workload based on composition. General medicine++: General medicine+ plus other contributing subs with segregated admissions data in SMRP. Dermatology not involved in Gen Med workload.*

<a href="#top">Return to table of contents</a>


## Case Study 2 - Drilldown HUS

```{r}
cases %>%
  filter(hospital=="UMUM SARAWAK") %>%
  kbl("html", align = "c", escape = F) %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 10, position = "center") %>%
  kable_paper(full_width = F) %>%
  column_spec(7, color = "white", bold = T,
              background = ifelse(cases$ES_current < 0, "red", "green"),
              popover = paste("am:", cases$Total)) %>%
  column_spec(9, color = "white", bold = T,
              background = ifelse(cases$ES_all < 0, "red", "green"),
              popover = paste("am:", cases$Total))
```

```{r cshus, message=FALSE, echo=FALSE, warning=FALSE}

urlcshus <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=1454553381"

cshus <- gsheet2tbl(urlcshus, "cs_hus")


cshus %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") %>%
  row_spec(1, color = "#150377")
#gm+ (Gastro, Endoc, Gery, Nephro, Pall)
```
*HUS workload based on composition. General medicine+: SMRP did not segragate data by subs; shared workload with existing contributing subs. General medicine++: General medicine+ plus other contributing subs with segregated admissions data in SMRP. Dermatology not involved in Gen Med workload.*

<a href="#top">Return to table of contents</a>

## Case Study 3 - Drilldown HKL

```{r}
cases %>%
  filter(hospital=="KUALA LUMPUR") %>% 
  kbl("html", align = "c", escape = F) %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 10, position = "center") %>%
  kable_paper(full_width = F) %>%
  column_spec(7, color = "white", bold = T,
              background = ifelse(cases$ES_current < 0, "red", "red"),
              popover = paste("am:", cases$Total)) %>%
  column_spec(9, color = "white", bold = T,
              background = ifelse(cases$ES_all < 0, "red", "green"),
              popover = paste("am:", cases$Total)) 

```

```{r cshkl, message=FALSE, echo=FALSE, warning=FALSE}

urlcshkl <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=898591304"

cshkl <- gsheet2tbl(urlcshkl, "cs_hkl")


cshkl %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") %>%
  row_spec(1:3, color = "#150377")
```
*HKL workload based on composition. General medicine+: SMRP did not segragate data by subs; shared workload with existing contributing subs.*

<a href="#top">Return to table of contents</a>

## Case Study 4 - Drilldown Serdang

```{r}
cases %>%
  filter(hospital=="SERDANG") %>%
  kbl("html", align = "c", escape = F) %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 10, position = "center") %>%
  kable_paper(full_width = F) %>%
  column_spec(7, color = "white", bold = T,
              background = ifelse(cases$ES_current < 0, "red", "green"),
              popover = paste("am:", cases$Total)) %>%
  column_spec(9, color = "white", bold = T,
              background = ifelse(cases$ES_all < 0, "red", "green"),
              popover = paste("am:", cases$Total))
```
  
```{r csserdang, message=FALSE, echo=FALSE, warning=FALSE}

urlcsserdang <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=57638925"

csserdang <- gsheet2tbl(urlcsserdang, "cs_serdang")


csserdang %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") %>%
  row_spec(1:2, color = "rgba(250,128,114,1)")
```
*Serdang workload based on composition. General medicine+: SMRP did not segragate data by subs; shared workload with existing contributing subs.*

<a href="#top">Return to table of contents</a>

## Case Study 5 - Drilldown Melaka

```{r}
cases %>%
  filter(hospital=="MELAKA") %>%
  kbl("html", align = "c", escape = F) %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 10, position = "center") %>%
  kable_paper(full_width = F) %>%
  column_spec(7, color = "white", bold = T,
              background = ifelse(cases$ES_current < 0, "red", "red"),
              popover = paste("am:", cases$Total)) %>%
  column_spec(9, color = "white", bold = T,
              background = ifelse(cases$ES_all < 0, "red", "red"),
              popover = paste("am:", cases$Total))
```

```{r csmelaka, message=FALSE, echo=FALSE, warning=FALSE}

urlcsmelaka <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=1173288709"

csmelaka <- gsheet2tbl(urlcsmelaka, "cs_melaka")


csmelaka %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") %>%
  row_spec(1, color = "#150377")
```
*Melaka workload based on composition. General medicine++: General medicine plus other contributing subs with segregated admissions data in SMRP. Dermatology not involved in Gen Med workload.*

<a href="#top">Return to table of contents</a>

## Case Study 6 - Drilldown TENGKU AMPUAN AFZAN

```{r}
cases %>%
  filter(hospital=="TENGKU AMPUAN AFZAN") %>%
  kbl("html", align = "c", escape = F) %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 10, position = "center") %>%
  kable_paper(full_width = F) %>%
  column_spec(7, color = "white", bold = T,
              background = ifelse(cases$ES_current < 0, "red", "green"),
              popover = paste("am:", cases$Total)) %>%
  column_spec(9, color = "white", bold = T,
              background = ifelse(cases$ES_all < 0, "red", "green"),
              popover = paste("am:", cases$Total))
```

```{r cshtaa, message=FALSE, echo=FALSE, warning=FALSE}

urlcshtaa <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=2057673234"

cshtaa <- gsheet2tbl(urlcshtaa, "cs_htaa")


cshtaa %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") %>%
  row_spec(1:3, color = "#150377")
```
*HTAA workload based on composition. General medicine+: SMRP did not segragate data by subs; shared workload with existing contributing subs.*

<a href="#top">Return to table of contents</a>

## Case Study 7 - Drilldown SULTANAH AMINAH

```{r}
cases %>%
  filter(hospital=="SULTANAH AMINAH") %>%
  kbl("html", align = "c", escape = F) %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 10, position = "center") %>%
  kable_paper(full_width = F) %>%
  column_spec(7, color = "white", bold = T,
              background = ifelse(cases$ES_current < 0, "red", "red"),
              popover = paste("am:", cases$Total)) %>%
  column_spec(9, color = "white", bold = T,
              background = ifelse(cases$ES_all < 0, "red", "red"),
              popover = paste("am:", cases$Total))
```

```{r cshsa, message=FALSE, echo=FALSE, warning=FALSE}

urlcshsa <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=2062444221"

cshsa <- gsheet2tbl(urlcshsa, "cs_hsa")


cshsa %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") %>%
  row_spec(1:2, color = "#150377")
```
*HSA workload based on composition. General medicine+: SMRP partially segragate data by subs; shared workload with some of the existing contributing subs. General medicine++: General medicine+ plus other contributing subs with segregated admissions data in SMRP. Dermatology & Cardiology are not involved in Gen Med workload.*

<a href="#top">Return to table of contents</a>

## Case Study 8 - Drilldown SEBERANG JAYA

```{r}
cases %>%
  filter(hospital=="SEBERANG JAYA") %>%
  kbl("html", align = "c", escape = F) %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 10, position = "center") %>%
  kable_paper(full_width = F) %>%
  column_spec(7, color = "white", bold = T,
              background = ifelse(cases$ES_current < 0, "red", "green"),
              popover = paste("am:", cases$Total)) %>%
  column_spec(9, color = "white", bold = T,
              background = ifelse(cases$ES_all < 0, "red", "red"),
              popover = paste("am:", cases$Total))
```

```{r cssj, message=FALSE, echo=FALSE, warning=FALSE}

urlcssj <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=1014959329"

cssj <- gsheet2tbl(urlcssj, "cs_sj")


cssj %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center") 
```
*Seberang Jaya workload based on composition. General medicine+: SMRP partially segragate data by subs; shared workload with some of the existing contributing subs. General medicine++: General medicine+ plus other contributing subs with segregated admissions data in SMRP. All subs are involved in Gen Med workload.*

<a href="#top">Return to table of contents</a>

## Case Study 9 - Drilldown SULTAN HJ AHMAD SHAH

```{r}
cases %>%
  filter(hospital=="SULTAN HJ AHMAD SHAH") %>%
  kbl("html", align = "c", escape = F) %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 10, position = "center") %>%
  kable_paper(full_width = F) %>%
  column_spec(7, color = "white", bold = T,
              background = ifelse(cases$ES_current < 0, "red", "red"),
              popover = paste("am:", cases$Total)) %>%
  column_spec(9, color = "white", bold = T,
              background = ifelse(cases$ES_all < 0, "red", "red"),
              popover = paste("am:", cases$Total))
```

```{r csshas, message=FALSE, echo=FALSE, warning=FALSE}

urlcsshas <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=250197512"

csshas <- gsheet2tbl(urlcsshas, "cs_shas")


csshas %>%
  kbl("html", align = "c") %>%
  kable_material(c("hover")) %>% 
  kable_styling(font_size = 12, position = "center")
```
*HOSHAS workload based on composition. General medicine+: SMRP did not segragate data by subs; shared workload with existing contributing subs. All subs are involved in Gen Med workload.*

<a href="#top">Return to table of contents</a>

<br>
$${Adequacy = {Std\;Workload}_{Current} - \displaystyle \left[{Std\;Workload}_{Median} \left( \displaystyle \frac{Workload}{1000}\right)\right]}$$
<br> 


#### from About.Rmd
```{r urlgensub2, include=FALSE}
urlgensub <- "https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=565087130"
  #"https://docs.google.com/spreadsheets/d/1SFtj8JD1JDLMUdUExFoovDt6uIAFh5pWSpxPzZ_xK1Q/edit#gid=710983312"  
gensub <- gsheet2tbl(urlgensub, "gen_subs") 
```
```{r, include=FALSE}
gensub$type <- as.factor(gensub$type)
gensub$type <- relevel(gensub$type, "state")

rownames(gensub) <- gensub$hospital

#col3 <- c(`state` = "#150377", `major` = "salmon", `minor` = "grey")

gensub$hospital <- factor(gensub$hospital,
                   levels = gensub$hospital)

datagensub <- arrange(gensub, type, desc(Subs_prop))

```
# Data table: General medicine & subspecialties staffing composition
```{r, results='asis', message=FALSE}
knitr::kable(datagensub[1:59,c(1,13:21,23:27)], caption = "Data table: General medicine & subspecialties staffing counts.", align = "c", font_size = 7) %>% 
  row_spec(1:14, color = "#150377") %>%
  row_spec(15:41, color = "salmon") %>% 
  row_spec(42:59, color = "grey") %>% 
  kableExtra::scroll_box(width = "100%")

#pander(hosp2019, justify = "center")
```
<a href="#top">Return to table of contents</a>
<br>
```{r, include=FALSE}
library(kableExtra)
datagensub %>%
  kbl("html") %>%
  kable_material(c("striped", "condensed", "scale_down")) %>% 
  kable_styling(font_size = 10) %>% 
  kableExtra::scroll_box(width = "100%")
```



